MSA Asthma Place of Service Timeseries

### 2019-03-23 r_scripts/analysis/asthma_place_of_service_analysis.Rmd
updated figure and results

```{r age_sameday}
age_results <- asthma_pos_list %>% 
  map_dfr(., function(df){
    service_place <- as.character(df$service_place[1])
    # complete case
    sex_df <- df %>% filter(!is.na(geo_smk10)) %>% 
      # nest strata
      nest(-age_cat) %>% 
      mutate(model = map(data, ~ clogit(outcome ~ geo_smk10 + wrf_temp +
                                          strata(identifier), data = .)),
             est_df = map(model, function(mod){
                  # n events
                  n_events <- mod$nevent
                  # odds ratio and 95% CI
                  estimates <- broom::tidy(mod) %>% 
                    filter(term == "geo_smk10") %>% 
                    dplyr::select(term, estimate, conf.low, conf.high) %>% 
                    mutate_at(2:4, funs(round(exp(.),3))) %>% 
                    cbind(service_place, n_events, .) %>% 
                    mutate(service_place = as.character(service_place))})) %>% 
      dplyr::select(-data, -model) %>% 
      unnest(est_df)
  }) %>% 
  rename(strata = age_cat) %>% 
  dplyr::select(strata, service_place:conf.high) %>%
   filter(n_events > 30) %>%
   filter(conf.high < 5)

@@

```{r all_results}
results <- bind_rows(sameday_result, sex_result, age_results) %>% 
  rename(odds_ratio = estimate, lower95 = conf.low, upper95 = conf.high) %>% 
  mutate(strata = case_when(strata == "Total" ~ "All Strata",
                            TRUE ~ strata),
         # shorten names of pos
         service_place = case_when(service_place=="Ambulance-Land"~"Ambulance",
          service_place == "Emergency Room – Hospital" ~ "Emergency Department",
          service_place == "Urgent Care Facility" ~ "Urgent Care",
          TRUE ~ service_place),
         # set order of strata
          strata = factor(strata, 
            levels = c("All Strata", "Female", "Male", "Age < 15", 
                       "Age 15-65", "Age > 65"))) %>% 
    # set order of service place
          # service_place = factor(service_place, 
          #   levels = c("SABA Fill", "Office", "Outpatient Hospital", 
          #              "Urgent Care", "Ambulance", "Emergency Room", 
          #              "Inpatient Hospital"))) %>% 
  # remove ambulance since it has so few observations
  filter(service_place %in% c("SABA Fill", "Office", "Urgent Care", "Ambulance",
                              "Emergency Department", "Outpatient Hospital", 
                              "Inpatient Hospital"))
```

@@

```{r plot}
plot <- ggplot(results, aes(x = strata, y = odds_ratio)) +
  geom_point(color = "#3c1053") + 
  geom_errorbar(aes(ymin=lower95, ymax=upper95), color = "#3c1053",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~service_place, scales = "free_y", ncol = 2) +
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in WFS PM"[2.5]))) +
  xlab("Stratum") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.7),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

>>>>

```{r age_sameday}

age_results <- asthma_pos_list %>% 
  map_dfr(., function(df){
    service_place <- as.character(df$service_place[1])
    # complete case
    age_df <- df %>% filter(!is.na(geo_smk10)) %>% 
      # nest strata
      nest(-age_cat) %>% 
      mutate(model = map(data, ~ clogit(outcome ~ geo_smk10 + wrf_temp +
                                          strata(identifier), data = .)),
             est_df = map(model, function(mod){
                  # n events
                  n_events <- mod$nevent
                  # odds ratio and 95% CI
                  estimates <- broom::tidy(mod) %>% 
                    filter(term == "geo_smk10") %>% 
                    dplyr::select(term, estimate, conf.low, conf.high) %>% 
                    mutate_at(2:4, funs(round(exp(.),3))) %>% 
                    cbind(service_place, n_events, .) %>% 
                    mutate(service_place = as.character(service_place))})) %>% 
      dplyr::select(-data, -model) %>% 
      unnest(est_df)
  }) %>% 
  rename(strata = age_cat) %>% 
  dplyr::select(strata, service_place:conf.high) %>%
   filter(n_events > 30) %>%
   filter(conf.high < 5) %>% 
  mutate(strata = paste0(strata, ' Yrs'))

@@

```{r all_results}
results <- bind_rows(sameday_result, sex_result, age_results) %>% 
  rename(odds_ratio = estimate, lower95 = conf.low, upper95 = conf.high) %>% 
  mutate(strata = case_when(strata == "Total" ~ "All Subjects",
                            TRUE ~ strata),
         # shorten names of pos
         service_place = case_when(service_place=="Ambulance-Land"~"Ambulance",
          service_place == "Emergency Room – Hospital" ~ "Emergency Department",
          service_place == "Urgent Care Facility" ~ "Urgent Care",
          TRUE ~ service_place),
         # set order of strata
          strata = factor(strata, 
            levels = c("All Subjects", "Female", "Male", "Age < 15 Yrs", 
                       "Age 15-65 Yrs", "Age > 65 Yrs"))) %>% 
    # set order of service place
          # service_place = factor(service_place, 
          #   levels = c("SABA Fill", "Office", "Outpatient Hospital", 
          #              "Urgent Care", "Ambulance", "Emergency Room", 
          #              "Inpatient Hospital"))) %>% 
  # remove ambulance since it has so few observations
  filter(service_place %in% c("SABA Fill", "Office", "Urgent Care", "Ambulance",
                              "Emergency Department", "Outpatient Hospital", 
                              "Inpatient Hospital"))
```

@@

```{r plot}
scaleFUN <- function(x) sprintf("%.2f", x)

plot <- ggplot(results, aes(x = strata, y = odds_ratio)) +
  geom_point(color = "#3c1053") + 
  geom_errorbar(aes(ymin=lower95, ymax=upper95), color = "#3c1053",width = 0.2) +
  geom_hline(yintercept = 1, linetype=2) +
  facet_wrap(~service_place, scales = 'free_y', ncol = 2) +
  scale_y_continuous(label = scaleFUN) + 
  ylab(expression(paste("Odds Ratio for 10µg/m"^3, " Increase in WFS PM"[2.5]))) +
  xlab("All Subjects and Specific Subgroups") +
   # plot theme
    theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    # strip element
    strip.background = element_rect(colour=NA, fill=NA),
    panel.border = element_rect(fill = NA, color = "black"),
    # facet text size
    strip.text = element_text(size = 10),
    # axis element (tilt)
    axis.text.x = element_text(angle = 45, hjust = 0.95, vjust = 0.95),
    #axis.title.x = element_blank(),
    #axis.ticks.x = element_blank(),
    axis.title.y = element_text(angle = 90))

### 2019-03-23 r_scripts/analysis/msa_asthma_timeseries.Rmd
updated figure and results

```{r saba_df}
saba <- read_csv("./data/health/2013-oregon_casecross_saba.csv") %>% 
  rename(identifier = personkey, ZIP = ZIPCODE) %>% 
  mutate(service_place = "SABA Fill",
         dx1 = ndc) %>% 
  # keeping only vars in the other casecrossover dataframes
  dplyr::select(vars_keep, ndc) %>% 
  # turn in to list
  list()

>>>>

```{r saba_df}
saba <- read_csv("../../data/health/2013-oregon_casecross_saba.csv") %>% 
  rename(identifier = personkey, ZIP = ZIPCODE) %>% 
  mutate(service_place = "SABA Fill",
         dx1 = ndc) %>% 
  # keeping only vars in the other casecrossover dataframes
  dplyr::select(vars_keep, ndc) %>% 
  # turn in to list
  list()
